---
title: "About Me"
---

::: panel-tabset

## Bio
I grew up in Melbourne, Australia and was exposed to the wonders of the natural world from a very young age. I quickly learned that understanding the natural world would be what I wanted to do for my career. My family moved to Dallas, Texas in 2008, where I would finish highschool as a remarkably average student. I attended the University of Arkansas for my undergraduate career, where the freedom to learn what I was interested in allowed me to explore my curiosities unbounded. I graduated with degrees in chemistry, biology, and environmental science along with minors in physics and math. I wanted a strong foundation in the hard sciences so I could eventually build up to study the Earth as a system. 

I graduated in May 2020, right as the coronavirus pandemic took off. I admittedly didn't what my next step was after my undergraduate career, and worked as a bartender for about a year and a half while doing research with Dr. Jihua Hao from the Blue Marble Space Institute of Science (BMSIS). We worked on modeling the thermodynamics of amino acid synthesis on Saturn's moon Enceladus - in an attempt to evaluate its potential for abiogenesis in its liquid water ocean beneath its icy crust.

I realized that I wanted a broader set of tools to be able to analyze data from the natural world. I decided that data science would be the perfect place to leverage the power of data and statistics to any problem I'm interested in, so I decided to attend UCSB's Master of Environmental Data Science program. 

I am broadly interested in many topics across the natural world. I enjoy learning about evolutionary biology, earth systems and planetary science, cosmology, climate science, and astrobiology

## Places Traveled

```{r}
#| include: false
source("map_script.R")
```

```{r}
#| echo: false
my_map
```
:::